sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2023-01-24 doc/paper-jss/owls.Rmd
Prep for paper submission

```{r fit-negb2, echo=TRUE, warning=FALSE}
fit_owl <- sdmTMB(count ~ 1 + nao + (1 | year_f),
  spatial_varying = ~ nao,
  time = "year",
  data = snow, 
  family = nbinom2(link = "log"),
  spatial = "on",
  spatiotemporal = "iid",
  mesh = mesh,
  reml = TRUE,
  silent = FALSE
)
```

@@

```{r owl-newton, results='hide'}
fit_owl2 <- run_extra_optimization(fit_owl, newton_loops = 1)
```

@@

```{r predict-owls, message=FALSE}
pred <- predict(fit_owl2)
set.seed(19208)
pred$resid <- residuals(fit_owl2)
```

>>>>

```{r fit-negb2, echo=TRUE, warning=FALSE, cache=TRUE, results='hide'}
fit_owl <- sdmTMB(count ~ 1 + nao + (1 | year_f),
  spatial_varying = ~ nao,
  time = "year",
  data = snow, 
  family = nbinom2(link = "log"),
  spatial = "on",
  spatiotemporal = "iid",
  mesh = mesh,
  reml = TRUE,
  silent = FALSE
)
```

@@

```{r owl-newton, results='hide', cache=TRUE}
fit_owl2 <- run_extra_optimization(fit_owl, newton_loops = 1)
```

@@

```{r predict-owls, message=FALSE, cache=TRUE}
pred <- predict(fit_owl2)
set.seed(19208)
pred$resid <- residuals(fit_owl2)
```

### 2023-01-24 doc/paper-jss/paper-jss.Rmd
Prep for paper submission

@@

```{r sdmTMB-lib0, eval=TRUE, echo=FALSE}
library(sdmTMB)
# simplify for paper:
pcod_original <- pcod # save it for later
pcod <- dplyr::select(pcod, year, density, depth, lon, lat) |>
  tibble::as_tibble()
```

```{r sdmTMB-lib, eval=TRUE, echo=TRUE}
library(sdmTMB)
head(pcod, n = 3)
```

@@

```{r child="pcod.Rmd", eval=TRUE}
```

```{r child="owls.Rmd", eval=TRUE}
```

```{r child="inla-comparison.Rmd", eval=TRUE}
```

```{r child="timing.Rmd", eval=TRUE}
```

>>>>

\pkg{sdmTMB} can be installed from the Comprehensive \proglang{R} Archive Network (CRAN) at <https://CRAN.R-project.org/package=sdmTMB>:

```{r sdmTMB-install, eval=FALSE, echo=TRUE}
install.packages("sdmTMB", dependencies = TRUE)
```

@@

```{r sdmTMB-lib0, eval=TRUE, echo=FALSE}
library("sdmTMB")
# simplify for paper:
pcod_original <- pcod # save it for later
pcod <- dplyr::select(pcod, year, density, depth, lon, lat) |>
  tibble::as_tibble()
```

```{r sdmTMB-lib, eval=TRUE, echo=TRUE}
library("sdmTMB")
head(pcod, n = 3)
```

@@

```{r child="pcod.Rmd", eval=TRUE, cache=TRUE}
```

```{r child="owls.Rmd", eval=TRUE, cache=TRUE}
```

```{r child="inla-comparison.Rmd", eval=TRUE, cache=TRUE}
```

```{r child="timing.Rmd", eval=TRUE, cache=TRUE}
```
